VIMC Antibody-Effector Assay Study: Ackerman Data
========================================================

Some text....

```{r loadPackages, message=FALSE, echo=FALSE}
rm(list=ls(all=TRUE))
setwd("~/FcR Assay Comparison Study/analysis/FinalStudy/code")
source("../macro/load_libraries.R")
load_libraries()
```


```{r ReadIn_Encryption, message=FALSE, echo=FALSE}
code = read.csv("../encryption_Ackerman/encryption.csv")
colnames(code) = tolower(colnames(code))
```

```{r ReadIn_AckermanData, message=FALSE, echo=FALSE}
man = read.csv("../qdata/FcRFinal_Ackerman_20130314.csv")
colnames(man) = tolower(colnames(man))
man = man[,c('assay_subtype','detectionreagent','bead_no','antigen_name','well_role','spec_type','sample','study_control_name',
             'name','standard_name','expconc','starting_concentration','dilution_factor','fi','fibkgd')]

man$assay_subtype = interaction("Acker", man$assay_subtype)

# Get all obs where well_role is Sample
man = man[man$well_role=="Unknown",]

# Put name into sample
man$sample = as.character(man$sample)
man$name = as.character(man$name)
man$sample = ifelse(man$name!="",man$name,man$sample)

# Sort data
man = man[with(man, order(sample,antigen_name,detectionreagent)),]

# Remove pilot study samples FCAC001 to FCAC010
man = man[!man$sample %in% c("FCAC001","FCAC002","FCAC003","FCAC004","FCAC005","FCAC006","FCAC007","FCAC008","FCAC009","FCAC010"),]

# Merge coding
man = merge(man, code, by.x=c("sample"),by.y="blinded_sample_id",all.x=TRUE)
man$group_assignment = as.character(man$group_assignment)
man$study_control_name = as.character(man$study_control_name)
man$group_assignment = ifelse(man$study_control_name=="IVIG", "IVIG", man$group_assignment)
man$group_assignment = ifelse(man$study_control_name=="HIVIG", "HIVIG & HIVIG-C", man$group_assignment)
man$group_assignment = ifelse(man$study_control_name=="HIVIG-C", "HIVIG & HIVIG-C", man$group_assignment)

# Change colnames
names(man)[names(man)=="assay_subtype"] = "Assay"
names(man)[names(man)=="group_assignment"] = "Group"

# Remove plasma samples
out = data.frame( do.call( rbind, strsplit( man$sample, ' ' ) ) ) 
names(out) = paste('column',1:2,sep="")
man = cbind(man, out)
man = man[man$column1!="Plasma",][,c(1:19)]

# Remove rows where Group is Blank
man = man[man$Group!="",]
# Order levels for Group variable
man$Group <- factor(man$Group, levels = c('CHRONIC Treated','chronic untreated','elite controller','VAX004','Placebo','HIV Seroneg','IVIG','HIVIG & HIVIG-C'),ordered = TRUE)

rm(out)
```


```{r ReadIn_MetaData_Ack, message=FALSE,echo=FALSE}
meta = read.csv("../qdata/FcRPilotStudy_AntigenMetadata_20130320.csv")
colnames(meta) = tolower(colnames(meta))
meta = meta[,c('antigenname_ackermanlab','beadnum_ackerman_fcr_final','study.specific.antigen.name','subtype')]

meta$aginfo = interaction(meta$study.specific.antigen.name, meta$subtype)
meta$aginfo = as.character(meta$aginfo)

# Conflict in HSV-1 and HSV-2. So resolve by making it HSV. 
meta$aginfo = ifelse(meta$aginfo=="HSV-2 gG.", "HSV gG.", meta$aginfo)

# Missing Study_Specific_Antigen_Name for "gp120 PVO"
meta$aginfo = ifelse(meta$aginfo==".B", "r.gp120 PVO.B", meta$aginfo)

# Merge man and meta
man = merge(man, meta, by.x=c("bead_no"),by.y="beadnum_ackerman_fcr_final",all.x=TRUE)
```


# Data
A total of n=152 fractionated purified IgG samples and n=10 unfractionated plasma samples along with n=12 monoclonal b12 mutants were evaluated in this study. The number of purified IgG samples in each group is provided below:
```{r table1, results='asis',echo=FALSE}
print(xtable(table(man$Group)/474,digit=0),include.colnames=F,type='html')
```

Here is the list of all 16 detection reagents: 
```{r table2, results='asis',echo=FALSE}
print(xtable(cbind(c("Total IgA", "Total IgG", rep("FcR",5),rep("IgG Subclass",4),rep("Lectin",5)),as.character(sort(unique(man$detectionreagent))))),include.colnames=F,type='html')
```

Here is the list of all 19 Env antigens: 
```{r table3, results='asis',echo=FALSE}
aglist_gp120 <- grep("gp120",unique(man$antigen_name),ignore.case=T,value=T)
aglist_gp140 <- grep("gp140",unique(man$antigen_name),ignore.case=T,value=T)
aglist_gp41 <- grep("gp41",unique(man$antigen_name),ignore.case=T,value=T)
aglist_SOSIP <- grep("SOSIP",unique(man$antigen_name),ignore.case=T,value=T)

print(xtable(cbind(c(rep("gp120", length(aglist_gp120)), rep("gp140",length(aglist_gp140)), rep("gp41",length(aglist_gp41)),rep("SOSIP",length(aglist_SOSIP))),c(aglist_gp120,aglist_gp140,aglist_gp41,aglist_SOSIP))),include.colnames=F,type='html')
```



# FI by Groups

```{r Boxplot_1_1_Ack,message=FALSE,echo=FALSE,fig.width=10, fig.height=7}
data = man

q = ggplot(data, aes(x=factor(Group), y=fi)) 
q + theme_bw()  + ylab("FI") + xlab("Groups") +
  #scale_y_log10(breaks=c(0.05, 1,10,50), labels=c(eval(cutoffexp),1,10,50)) +
  scale_y_log10() +
  #geom_point(size=2,position = position_jitter(width = 0.2, height=0),aes(colour = factor(response)))  +
  geom_point(size=2,position = position_jitter(width = 0.2, height=0), colour="#FF9900")  +
  geom_boxplot(outlier.colour = "NA",alpha=0) +  
  theme(plot.margin = unit(c(1,1,0,1), "cm"),legend.position="bottom",
       legend.title=element_text(size=7,vjust=-1.6),
       legend.text=element_text(size=7,vjust=-1.6),
       axis.text.x = element_text(size=11,angle = 45, hjust = 1,vjust=0.95), 
       axis.text.y = element_text(size=11), 
       axis.title.x = element_text(size=14), 
       axis.title.y = element_text(angle=90, size=14,vjust=-0.4), 
       strip.text.x = element_text(size = 7), 
       strip.text.y = element_text(size = 12, face="bold", angle=270))   
```

# FIBkgd by Groups

```{r Boxplot_1_2_Ack,message=FALSE,echo=FALSE,warning=FALSE,fig.width=10, fig.height=7}

q = ggplot(data, aes(x=factor(Group), y=fibkgd)) 
q + theme_bw()  + ylab("FIBkgd") + xlab("Groups") +
  #scale_y_log10(breaks=c(0.05, 1,10,50), labels=c(eval(cutoffexp),1,10,50)) +
  scale_y_log10() +
  #geom_point(size=2,position = position_jitter(width = 0.2, height=0),aes(colour = factor(response)))  +
  geom_point(size=2,position = position_jitter(width = 0.2, height=0), colour="#FF9900")  +
  geom_boxplot(outlier.colour = "NA",alpha=0) +  
  theme(plot.margin = unit(c(1,1,0,1), "cm"),legend.position="bottom",
       legend.title=element_text(size=7,vjust=-1.6),
       legend.text=element_text(size=7,vjust=-1.6),
       axis.text.x = element_text(size=11,angle = 45, hjust = 1,vjust=0.95), 
       axis.text.y = element_text(size=11), 
       axis.title.x = element_text(size=14), 
       axis.title.y = element_text(angle=90, size=14,vjust=-0.4), 
       strip.text.x = element_text(size = 7), 
       strip.text.y = element_text(size = 12, face="bold", angle=270))

rm(data)
```


# Correlation Heatmap for all Antigens (Conjugate: ahuigg): Ackerman data

```{r CorrHeatMap_1_Ack, message=FALSE,echo=FALSE,warning=FALSE,fig.width=12,fig.height=12}
ahuigg = man[man$detectionreagent=="ahuIgG",]
data = ahuigg[,c("sample","Assay","aginfo","spec_type","study_control_name","name","standard_name","expconc",
                        "starting_concentration","dilution_factor","fi","unblinded_sample_id","Group")]

ahuigg.wide = dcast(data, sample + Assay + Group + spec_type + study_control_name + name + standard_name + expconc + 
                          starting_concentration + dilution_factor + unblinded_sample_id ~ aginfo, value.var="fi")

cormat = cor(as.matrix(ahuigg.wide[,12:49]), method = "spearman")
par(oma=c(10,0,0,10))
par(mar=c(0,0,0,0))
pairs.breaks = seq(-1, 1, by=0.1)
#length(pairs.breaks)
mycol = colorpanel(n=20,low="green",mid="black", high="red")
#length(mycol)
hm = borate_heatmap(cormat, breaks=pairs.breaks, col=mycol, symm=TRUE, trace="none",cexCol=1.0,cexRow=1.0)
```

# Heatmap FI for Sample vs Antigen (for ahuigg): Ackerman data

```{r CorrHeatMap_2_Ack, message=FALSE,echo=FALSE,warning=FALSE,fig.width=14,fig.height=10}

# Heatmap for Sample vs Readout
data = ahuigg.wide[,c(3,12:49)]
#rownames(data) = data$Group
rownames(data) = make.unique(as.character(data$Group))
data = data[,2:39]
datascaled = as.matrix(scale(data))
datascaled1 = as.data.frame(t(datascaled))
datascaled1 = as.matrix(datascaled1)
par(oma=c(0,0,0,8))
par(mar=c(0,0,0,0))
hm999 = borate_heatmap(datascaled1, breaks=pairs.breaks, col=mycol, scale='none',trace="none", cexCol=0.5,cexRow=1.0)
rm(data,datascaled,datascaled1,hm999)
```


# Correlation Matrices for each Detection Reagent (using 120 samples)

## Detection Reagent: FcgRIIa
```{r Corr_1_FcgRIIa, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

#Make Correlation Matrix with Scatter Plot
corrman = man[man$aginfo %in% c("r.gp120 BaL (293T/Lewis).B","r.gp120 Du151 (HEK 293).C","r.gp120 JRCSF (HEK 293).B","r.gp120 TRO (HEK 293).B",
                          "r.gp120 CM235 (HEK 293).CRF01_AE","r.gp120 Du156.12 (HEK 293).C","r.gp120 MN (HEK 293).B","r.gp120 YU2 (HEK 293).B",
                          "r.gp120 93TH975 (insect).CRF01_AE","r.gp120 CM235 (insect).CRF01_AE","r.gp120 IIIB (CHO).B","r.gp120 PVO.B",
                          "r.gp120 ZM109F.PB4 (HEK 293).C","r.gp140_aa24-680 Bal1A (trimer/HEK 293).B","r.gp140 SF162 (HEK 293).B",
                          "SOSIP.","r.gp140 CN54 (CHO/ARRRP).CRF07_BC","r.gp41_aa23-170 HxBc2 (HEK 293).B","r.gp140 Du151 (HEK 293).C"),]

corrman = corrman[corrman$Group %in% c("CHRONIC Treated","chronic untreated","elite controller","VAX004"),]
corrman$Group = as.factor(as.character(corrman$Group))

panel.spearman <- function(x, y, cex.cor, ...) {
  horizontal <- (par("usr")[1] + par("usr")[2]) / 2;
  vertical <- (par("usr")[3] + par("usr")[4]) / 2;
  r <- round(cor(x, y,method="spearman"),digits=2)
  txt <- format(r)
  pval = as.double(unlist(cor.test(x, y, method="spearman", alternative="two.sided")[3]))
  #txt2 <- format(pval, digits=2)
  #text(horizontal, vertical, txt, cex=3*r)
  #text(horizontal, vertical-0.2, txt2, cex=3*(1-pval))
  text(horizontal, vertical, txt, cex=max(0.5, 2*(1-pval)))
}

mydiag.panel <- function(x, ...){  
  ll <- par("usr") 
  rect(ll[1], ll[3], ll[2], ll[4], col="#FDFF65") 
}

corrman1 = corrman[corrman$detectionreagent=="FcgRIIa",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    
                            "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                            "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                            "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                            "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",       "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                            "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                            "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```


## Detection Reagent: FcgRIIIb
```{r Corr_1_FcgRIIIb, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="FcgRIIIb",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    
                   "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                   "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                   "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                   "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",       "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                   "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                   "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```


## Detection Reagent: ahuIgA
```{r Corr_1_ahuIgA, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="ahuIgA",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    
                   "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                   "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                   "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                   "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",       "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                   "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                   "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```


## Detection Reagent: FcgRIIb
```{r Corr_1_FcgRIIb, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="FcgRIIb",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    
                   "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                   "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                   "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                   "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",       "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                   "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                   "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```


## Detection Reagent: FcgRIIIa
```{r Corr_1_FcgRIIIa, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="FcgRIIIa",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    
                   "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                   "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                   "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                   "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",       "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                   "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                   "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```


## Detection Reagent: MBL
```{r Corr_1_MBL, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="MBL",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    
                   "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                   "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                   "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                   "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",       "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                   "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                   "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```


## Detection Reagent: VVL
```{r Corr_1_VVL, message=FALSE,echo=FALSE,warning=FALSE,fig.width=8,fig.height=8}

corrman1 = corrman[corrman$detectionreagent=="VVL",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \nBaL \n(293T/Lewis)\n.B",     "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                            "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```

## Detection Reagent: PNA
```{r Corr_1_PNA, message=FALSE,echo=FALSE,warning=FALSE,fig.width=8,fig.height=8}

corrman1 = corrman[corrman$detectionreagent=="PNA",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \nBaL \n(293T/Lewis)\n.B",     "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                            "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```

## Detection Reagent: SNA
```{r Corr_1_SNA, message=FALSE,echo=FALSE,warning=FALSE,fig.width=8,fig.height=8}

corrman1 = corrman[corrman$detectionreagent=="SNA",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \nBaL \n(293T/Lewis)\n.B",     "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                            "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```

## Detection Reagent: LCA
```{r Corr_1_LCA, message=FALSE,echo=FALSE,warning=FALSE,fig.width=8,fig.height=8}

corrman1 = corrman[corrman$detectionreagent=="LCA",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \nBaL \n(293T/Lewis)\n.B",     "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                            "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```

## Detection Reagent: FcgRI
```{r Corr_1_FcgRI, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="FcgRI",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    "r.gp120 \nCM235 \n(HEK 293).\nCRF01_AE",
                             "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                             "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                             "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                             "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",      "r.gp140_aa24-680 \nBal1A \n(trimer/HEK 293)\n.B", "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                             "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                             "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```

## Detection Reagent: IgG1
```{r Corr_1_IgG1, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="IgG1",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    "r.gp120 \nCM235 \n(HEK 293).\nCRF01_AE",
                             "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                             "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                             "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                             "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",      "r.gp140_aa24-680 \nBal1A \n(trimer/HEK 293)\n.B", "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                             "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                             "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```



## Detection Reagent: ahuIgG
```{r Corr_1_ahuIgG, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="ahuIgG",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    "r.gp120 \nCM235 \n(HEK 293).\nCRF01_AE",
                             "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                             "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                             "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                             "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",      "r.gp140_aa24-680 \nBal1A \n(trimer/HEK 293)\n.B", "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                             "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                             "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```

## Detection Reagent: IgG2
```{r Corr_1_IgG2, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="IgG2",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    "r.gp120 \nCM235 \n(HEK 293).\nCRF01_AE",
                             "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                             "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                             "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                             "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",      "r.gp140_aa24-680 \nBal1A \n(trimer/HEK 293)\n.B", "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                             "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                             "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```

## Detection Reagent: IgG3
```{r Corr_1_IgG3, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="IgG3",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    "r.gp120 \nCM235 \n(HEK 293).\nCRF01_AE",
                             "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                             "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                             "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                             "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",      "r.gp140_aa24-680 \nBal1A \n(trimer/HEK 293)\n.B", "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                             "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                             "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```

## Detection Reagent: IgG4
```{r Corr_1_IgG4, message=FALSE,echo=FALSE,warning=FALSE,fig.width=17,fig.height=12}

corrman1 = corrman[corrman$detectionreagent=="IgG4",]
corrman1.wide = dcast(corrman1, sample ~ aginfo, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
colnames(corrman1.wide) = c("r.gp120 \n93TH975 \n(insect).\nCRF01_AE",   "r.gp120 \nBaL \n(293T/Lewis)\n.B",    "r.gp120 \nCM235 \n(HEK 293).\nCRF01_AE",
                             "r.gp120 \nCM235 \n(insect).\nCRF01_AE",     "r.gp120 \nDu151 \n(HEK 293)\n.C",     "r.gp120 \nDu156.12 \n(HEK 293)\n.C",
                             "r.gp120 \nIIIB \n(CHO)\n.B",                "r.gp120 \nJRCSF \n(HEK 293)\n.B",     "r.gp120 \nMN \n(HEK 293)\n.B",
                             "r.gp120 \nPVO.B",                       "r.gp120 \nTRO \n(HEK 293)\n.B",       "r.gp120 \nYU2 \n(HEK 293)\n.B",                  
                             "r.gp120 \nZM109F.PB4 \n(HEK 293)\n.C",      "r.gp140_aa24-680 \nBal1A \n(trimer/HEK 293)\n.B", "r.gp140 \nCN54 \n(CHO/ARRRP).\nCRF07_BC",        
                             "r.gp140 \nDu151 \n(HEK 293)\n.C",           "r.gp140 \nSF162 \n(HEK 293)\n.B",     "r.gp41_aa23-170 \nHxBc2 \n(HEK 293)\n.B",        
                             "SOSIP.")

pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=0.8)
```


# Correlation Matrices for each Antigen

## Antigen: r.gp120 CM235 (insect).CRF01_AE
```{r Corr_1_antigen1, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 CM235 (insect).CRF01_AE",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 93TH975 (insect).CRF01_AE
```{r Corr_1_antigen2, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 93TH975 (insect).CRF01_AE",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 IIIB (CHO).B
```{r Corr_1_antigen3, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 IIIB (CHO).B",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp41_aa23-170 HxBc2 (HEK 293).B
```{r Corr_1_antigen4, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp41_aa23-170 HxBc2 (HEK 293).B",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 PVO.B
```{r Corr_1_antigen5, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 PVO.B",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 YU2 (HEK 293).B
```{r Corr_1_antigen6, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 YU2 (HEK 293).B",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp140 CN54 (CHO/ARRRP).CRF07_BC
```{r Corr_1_antigen7, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp140 CN54 (CHO/ARRRP).CRF07_BC",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: SOSIP.
```{r Corr_1_antigen8, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="SOSIP.",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp140_aa24-680 Bal1A (trimer/HEK 293).B
```{r Corr_1_antigen9, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp140_aa24-680 Bal1A (trimer/HEK 293).B",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 TRO (HEK 293).B
```{r Corr_1_antigen10, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 TRO (HEK 293).B",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 Du156.12 (HEK 293).C
```{r Corr_1_antigen11, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 Du156.12 (HEK 293).C",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 JRCSF (HEK 293).B
```{r Corr_1_antigen12, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 JRCSF (HEK 293).B",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 BaL (293T/Lewis).B
```{r Corr_1_antigen13, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 BaL (293T/Lewis).B",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 MN (HEK 293).B
```{r Corr_1_antigen14, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 MN (HEK 293).B",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 Du151 (HEK 293).C
```{r Corr_1_antigen15, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 Du151 (HEK 293).C",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp140 SF162 (HEK 293).B
```{r Corr_1_antigen16, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp140 SF162 (HEK 293).B",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp140 Du151 (HEK 293).C
```{r Corr_1_antigen17, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp140 Du151 (HEK 293).C",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 ZM109F.PB4 (HEK 293).C
```{r Corr_1_antigen18, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 ZM109F.PB4 (HEK 293).C",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```

## Antigen: r.gp120 CM235 (HEK 293).CRF01_AE
```{r Corr_1_antigen19, message=FALSE,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
corrman1 = corrman[corrman$aginfo=="r.gp120 CM235 (HEK 293).CRF01_AE",]
corrman1.wide = dcast(corrman1, sample ~ detectionreagent, value.var="fi")
corrman1.wide = corrman1.wide[,-1]
corrman1.wide = corrman1.wide[,order(names(corrman1.wide))]
pairs(corrman1.wide, cex.labels=1.2, diag.panel=mydiag.panel,label.pos=0.5,lower.panel=panel.spearman, gap=0, xaxt='n',yaxt='n',pch=20,cex=2)
```





